Does the COMPAS Needle Always Point Towards Equity? Finding Fairness in the COMPAS Risk Assessment Algorithm: A Case Study

### 2022-04-27 Paper_Draft2/Draft2.Rmd

```{r, include = FALSE}
x <- tribble(~`Two Year Recidivism by Race`, ~`Recidivated`, ~`Survived`,
             "African American", "1661", "1512",
             "Caucasian", "822", "1278")
```

>>>>

```{r, include = FALSE}
x <- tribble(~`Two Year Recidivism by Race`, ~`Recidivated`, ~`Survived`, ~`Total`,
             "African American", 1661, 1512, 3173,
             "Caucasian", 822, 1278, 2100,
             "Total", 2483, 2790, 5273)
```
